Toxic code snippets on Stack Overflow

### 2017-10-12 cloverflow-tse/cloverflow.tex
Latest changes.

\title{Outdated and License-Violating Code on Stack Overflow}

\author{Chaiyong Ragkhitwetsagul,~Matheus Paixao,~Jens Krinke,~Giuseppe Bianco,~Rocco Oliveto}

@@

The findings from our online survey of Stack Overflow answerers show that code
reusing activity occurs on Stack Overflow, just like in software. Stack Overflow
answerers occasionally clone code from other locations, such as their personal
projects, company projects, and open source projects, to Stack Overflow answers
as a solution or to complement their answer~\FIXME{put a precise number here}.
One participants says

\begin{quote}\textit{The real issue is less about the amount the code snippets
		on SO than it is about the staggeringly high number of software
		``professionals'' that mindlessly use them without understanding what they're
		copying, and the only slightly less high number of would-be professionals that
		post snippets with built-in security issues.  A related topic is beginners who
		post (at times dangerously) misleading tutorials online on topics they actually
		know very little about. Think PHP/MySQL tutorials written 10+ years after
		\texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that
		got posted the other day on HackerNew
		(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
		toxic code snippets.}\end{quote}

@@

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.2cm}lrrr}
			\toprule
			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
			\midrule
			Compatible & No license & No license & 28 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 28 & & \\
			\midrule
			Incompat. & No license & Apache-2 & 55 & & \\
			          & No license & BSD-3 & 1 & & \\
			          & No license & CDDLorGPLv2 & 1 & & \\
			          & No license & EPLv1 & 19 & & \\
			          & No license & GPLv2+/3+ & 6 & & \\
			          & No license & LesserGPLv2.1+/3+ & 20 & & \\
			          & No license & Unknown & 24 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 154 & & \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
In our study, we reveal another type of toxic code snippets which is software
licensing issues caused by code cloned to Stack Overflow. We found evidence that
154 pieces of code have been copied from Qualitas projects to Stack Overflow as
examples. Their status of accepted answers increase their chances of being
reused. Even though most of the Qualitas projects came with a software license,
we found that the license information were frequently missing after the code was
copied to Stack Overflow. The licensing terms on top of source code files are
not copied because usually only a small part of the file was cloned. In overall,
we can see that most of the Stack Overflow snippets do not contain licensing
terms while their clone counterparts in Qualitas projects do. The summary of
licensing information is listed in \Cref{tab:license_abc}.

>>>>

\title{Toxic code snippets on Stack Overflow}

\author{Chaiyong Ragkhitwetsagul,~Jens Krinke,~Matheus Paixao,~Giuseppe Bianco,~Rocco Oliveto}

@@

The findings from our online survey of Stack Overflow answerers show that code
reusing activity occurs on Stack Overflow, just like in software. Stack Overflow
answerers occasionally clone code from other locations, such as their personal
projects, company projects, and open source projects, to Stack Overflow answers
as a solution or to complement their answer~\FIXME{put a precise number here}.
One participants says:

\begin{quote}\textit{``The real issue is less about the amount the code snippets
		on SO than it is about the staggeringly high number of software
		``professionals'' that mindlessly use them without understanding what they're
		copying, and the only slightly less high number of would-be professionals that
		post snippets with built-in security issues.  A related topic is beginners who
		post (at times dangerously) misleading tutorials online on topics they actually
		know very little about. Think PHP/MySQL tutorials written 10+ years after
		\texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that
		got posted the other day on HackerNew
		(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
		toxic code snippets.''}\end{quote}

@@

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.2cm}lrrr}
			\toprule
			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
			\midrule
			Compatible & Apache-2 & Apache-2 & 1 & & \\
								  & EPLv1 & EPLv1 & 2 & & \\
								  & No license & No license	& 20 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 23 & & \\
			\midrule
			Incompat. & No license & EPLv1	& 10 & & \\
								& No license & GPLv2/2+/3+	& 7 & & \\
								& No license & AGPLv3 & 1 & & \\
								& No license & Apache-2 & 46 & & \\
								& No license & BSD/BSD3	& 4 & & \\
								& No license & LesserGPL/v2.1+/v3+ & 17 & & \\
								& spdxBSD3 & LesserGPLv2.1+	& 1 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 86 & & \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

%If developers copy and reuse these licensed pieces of code in their projects,
% conflicts may happen without their realisation.
In our study, we reveal another type of toxic code snippets which is software
licensing issues caused by code cloned to Stack Overflow. We found evidence that
154 pieces of code have been copied from Qualitas projects to Stack Overflow as
examples. Their status of accepted answers increase their chances of being
reused. Even though most of the Qualitas projects came with a software license,
we found that the license information were frequently missing after the code was
copied to Stack Overflow. The licensing terms on top of source code files are
not copied because usually only a small part of the file was cloned. In overall,
we can see that most of the Stack Overflow snippets do not contain licensing
terms while their clone counterparts in Qualitas projects do. 
Pleaste note that the
results here are analysed at file level, not clone fragment, thus there are some
clone pairs that share the same result and we combine them into a single pair.
The summary of
licensing information is listed in \Cref{tab:license_abc}.
